%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Software Engineer} % Job title
{JSI Telecom} % Organization
{Ottawa, Canada} % Location
{March 2015 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
  \item {Designed and implemented several advanced distributed search, filtering and sorting algorithms using Apache Lucene/Solr and Cassandra. These algorithms are capable of effeciently performing operations on billions of data records across hundreds of nodes.}
  \item {Applied machine learning techniques to solve classification problems involving big data.}
  \item {Used natural language processing techniques to solve linguistic classification problems involving big data.}
  \item {Built many advanced graphical features using WPF for a client application.}
\end{cvitems}
}

%------------------------------------------------   
\vspace{-2.5ex}
\cventry
{Software Engineer} % Job title
{Nanometrics} % Organization
{Ottawa, Canada} % Location
{July 2014 - March 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
  \item {Performed theoretical work to analyze the complexity of the various data acquisition patterns encountered by the time-series database built and maintained by the company.}
  \item {Used results of theoretical work to design algorithms that optimize the way in which data is consumed when the system is under heavy load.}
  \item {Designed a new threading and synchronization model for the database to increase its scalability.}
\end{cvitems}
}

%------------------------------------------------

\vspace{-4ex}

%------------------------------------------------    

\end{cventries}
